### 2019-11-20 README.Rmd
updated README + wordcounts

Missingness in outcomes was associated with multiple demographic variables. These associations could not be generalised, preventing a systematic approach to dealing with missingness. The identified associations may induce bias, meaning that complete case analysis should not be used for this data source - or other similar surveillance data. Our findings should be used motivate the use of imputation and to inform the specification of imputation models for similar surveillance data.

>>>>

Missingness in outcomes was associated with multiple demographic variables. These associations could not be generalised, preventing a systematic approach to dealing with missingness and indicating that domain knowledge is required. The identified associations may induce bias, meaning that multiple imputation may be beneficial for analyse using this data source - or other similar surveillance data. Our findings should be used to motivate the use of imputation and to inform the specification of imputation models that include auxiliary variables.
